Document Expansion with External Collections for Information Retrieval

### 2016-09-16 paper.tex
added single expansion runs, need to work on formatting

\begin{table}[htbp]
\centering
\begin{tabular}{|c|l|c|c|} \hline
{\bf Collection} & {\bf Run} & {\bf MAP} & {\bf nDCG@20} \\ \hline\hline
\rule{0pt}{2.5ex} \multirow{3}{*}{AP} & {\it baseline-ql} & 0.2337 & 0.4170 \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it baseline-rm} & 0.3298 ($\alpha=0.2$) & 0.4852 ($\alpha=0.3$) \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it baseline-rm-cv} & 0.3291 & 0.4858 \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it exp-ql} & 0.2799 & 0.4687 \\ \hline\hline
\rule{0pt}{2.5ex} \multirow{3}{*}{Robust} & {\it baseline-ql} & 0.2185 & 0.3825 \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it baseline-rm} & 0.2349 ($\alpha=0.2$) & 0.3893 ($\alpha=0.6$) \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it baseline-rm-cv} & 0.2663 & 0.3940 \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it exp-ql} & 0.2420 & 0.4066$^{\uparrow}$ \\ \hline\hline
\rule{0pt}{2.5ex} \multirow{3}{*}{wt10g} & {\it baseline-ql} & 0.1687 & 0.2753 \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it baseline-rm} & 0.1735 ($\alpha=0.7,0.8$) & 0.2738 ($\alpha=1.0$)\\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it baseline-rm-cv} & 0.1683 & 0.2633 \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it exp-ql} & 0.1836 & 0.3181$^{\uparrow\Uparrow}$ \\ \hline\hline
\rule{0pt}{2.5ex} \multirow{3}{*}{blogs06} & {\it baseline-ql} & 0.3064 & 0.2415 \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it baseline-rm} & 0.3103 ($\alpha=0.7$) & 0.2431 ($\alpha=1.0$)\\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it baseline-rm-cv} & 0.3064 & 0.2330 \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it exp-ql} & 0.2990 & 0.2343 \\ \hline\hline
\rule{0pt}{2.5ex} \multirow{3}{*}{clueweb09} & {\it baseline-ql} & 0.1117 & 0.1944 \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it baseline-rm} & 0.1163 ($\alpha=0.2$) & 0.2034 ($\alpha=0.7$) \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it baseline-rm-cv} & ?? & ?? \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it exp-ql} & 0.1183$^{\uparrow}$ & 0.2100 \\ \hline
\end{tabular}
\caption{The top-scoring runs and baselines by MAP. $\uparrow$ indicates statistically significant improvements over the oracle RM3 baseline, \textit{baseline-rm}, while $\Uparrow$ indicates statistically significant improvement and decrease compared to the cross validated RM3 baseline, \textit{baseline-rm-cv}. Significance at $p < 0.05$.}
\label{table.performance}
\end{table}

@@

\begin{table}[htbp]
\centering
\begin{tabular}{|l|c|c|c|c|} \hline
& \multicolumn{2}{c}{Self} & \multicolumn{2}{|c|}{Wikipedia} \\ \hline
{\bf Collection} & {\bf $\lambda$} & {\bf MAP} & {\bf $\lambda$} & {\bf MAP} \\ \hline
AP & ? & ? & 0.2 & 0.2662 \\ \hline
Robust & ? & ? & 0.2 & 0.2354 \\ \hline
wt10g & ? & ? & ? & ? \\ \hline
blogs06 & ? & ? & ? & ? \\ \hline
clueweb09 & ? & ? & ? & ? \\ \hline
\end{tabular}
\caption{The top-scoring runs by MAP using only one collection of expansion documents. ``Self'' indicates expansion using the document's original collection while ``Wikipedia'' indicates expansion using Wikipedia.}
\label{table.performance.single}
\end{table}

>>>>

\begin{table}[htbp]
\centering
\begin{tabular}{|c|l|c|c|} \hline
{\bf Collection} & {\bf Run} & {\bf MAP} & {\bf nDCG@20} \\ \hline\hline
\rule{0pt}{2.5ex} \multirow{3}{*}{AP} & {\it baseline-ql} & 0.2337 & 0.4170 \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it baseline-rm} & 0.3298 ($\alpha=0.2$) & 0.4852 ($\alpha=0.3$) \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it baseline-rm-cv} & 0.3291 & 0.4858 \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it exp-ql} & 0.2799 & 0.4687 \\ \hline\hline
\rule{0pt}{2.5ex} \multirow{3}{*}{Robust} & {\it baseline-ql} & 0.2185 & 0.3825 \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it baseline-rm} & 0.2349 ($\alpha=0.2$) & 0.3893 ($\alpha=0.6$) \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it baseline-rm-cv} & 0.2663 & 0.3940 \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it exp-ql} & 0.2420 & 0.4066$^{\uparrow}$ \\ \hline\hline
\rule{0pt}{2.5ex} \multirow{3}{*}{wt10g} & {\it baseline-ql} & 0.1687 & 0.2753 \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it baseline-rm} & 0.1735 ($\alpha=0.7,0.8$) & 0.2738 ($\alpha=1.0$)\\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it baseline-rm-cv} & 0.1683 & 0.2633 \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it exp-ql} & 0.1836 & 0.3181$^{\uparrow\Uparrow}$ \\ \hline\hline
\rule{0pt}{2.5ex} \multirow{3}{*}{blogs06} & {\it baseline-ql} & 0.3064 & 0.2415 \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it baseline-rm} & 0.3103 ($\alpha=0.7$) & 0.2431 ($\alpha=1.0$)\\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it baseline-rm-cv} & 0.3064 & 0.2330 \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it exp-ql} & 0.2990 & 0.2343 \\ \hline\hline
\rule{0pt}{2.5ex} \multirow{3}{*}{clueweb09} & {\it baseline-ql} & 0.1117 & 0.1944 \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it baseline-rm} & 0.1163 ($\alpha=0.2$) & 0.2034 ($\alpha=0.7$) \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it baseline-rm-cv} & ?? & ?? \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it exp-ql} & 0.1183$^{\uparrow}$ & 0.2100 \\ \hline
\end{tabular}
\caption{The top-scoring runs and baselines by MAP. $\uparrow$ indicates statistically significant improvements over the oracle RM3 baseline, \textit{baseline-rm}, while $\Uparrow$ indicates statistically significant improvement compared to the cross validated RM3 baseline, \textit{baseline-rm-cv}. Significance at $p < 0.05$.}
\label{table.performance}
\end{table}

@@

\begin{table}[htbp]
\centering
\begin{tabular}{|l|c|c|c|c|} \hline
Self & Wikipedia \\ \hline
{\bf Collection} & {\bf MAP} & {\bf MAP} \\ \hline
AP & 0.1898$^{\downarrow}$ & 0.1880$^{\downarrow}$ \\ \hline
Robust & 0.1922$^{\downarrow}$ & 0.1915$^{\downarrow}$ \\ \hline
wt10g & 0.1383$^{\downarrow}$ & 0.1396$^{\downarrow}$ \\ \hline
blogs06 & 0.1244$^{\downarrow}$ & 0.1261$^{\downarrow}$ \\ \hline
clueweb09 & ? & ? \\ \hline
\end{tabular}
\caption{The top-scoring runs by MAP using only one collection of expansion documents. ``Self'' indicates expansion using the document's original collection while ``Wikipedia'' indicates expansion using Wikipedia. $^{\downarrow}$ indicates statistically significant decreases compared to the corresponding run using two collections.}
\label{table.performance.single.map}
\end{table}

\begin{table}[htbp]
\centering
\begin{tabular}{|l|c|c|c|c|} \hline
Self & Wikipedia \\ \hline
{\bf Collection} & {\bf nDCG@20} & {\bf nDCG@20} \\ \hline
AP & 0.4236$^{\downarrow}$ & 0.4203$^{\downarrow}$ \\ \hline
Robust & 0.3832$^{\downarrow}$ & 0.3821$^{\downarrow}$ \\ \hline
wt10g & 0.2748$^{\downarrow}$ & 0.2753 \\ \hline
blogs06 & 0.2418$^{\downarrow}$ & 0.2418$^{\downarrow}$ \\ \hline
clueweb09 & ? & ? \\ \hline
\end{tabular}
\caption{The top-scoring runs by nDCG@20 using only one collection of expansion documents. ``Self'' indicates expansion using the document's original collection while ``Wikipedia'' indicates expansion using Wikipedia. $^{\downarrow}$ indicates statistically significant decreases compared to the corresponding run using two collections.}
\label{table.performance.single.ndcg}
\end{table}

To justify the use of multiple external collections, we expand documents using each of the expansion collections individually. These results are shown in Tables \ref{table.performance.single.map} and \ref{table.performance.single.ndcg}.
